Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-10 paper/tex/data.tex
consistency with methods

To assign an SED to each galaxy, the Adding Density Dependent Spectral Energy Distributions (\texttt{ADDSEDS}, deRose in prep.)\footnote{\url{https://github.com/vipasu/addseds}} procedure was used.
\texttt{ADDSEDS} uses a sample of $\sim 5\times 10^{5}$ galaxies from the magnitude-limited \sdss\ Data Release 6 Value Added Galaxy Catalogue \citep{Blanton:05} to train an empirical relation between absolute $r$-band magnitude, local galaxy density, and SED.
Each \sdss\ spectrum is parameterized by five weights corresponding to a weighted sum of five basis SED components using the \texttt{k-correct \red{v4\_3?}} software package\footnote{\url{http://kcorrect.org}} \citep{Blanton:07}.

@@

Following the findings of \citet{Bernstein:10}, \citet{Masters:2017} that only $~10^{4}$ spectra are necessary to calibrate \pz s to Stage IV requirements, we aimed to set aside a randomly selected training set of $3-5\times 10^{4}$ galaxies, $\sim 10\%$ of the full sample.
After all cuts described above, we designated a training set of $44\,404$ galaxies for which both photometry and redshifts would be provided to data-driven codes and a blinded test set of $399\,356$ galaxies for which photometry alone would be provided to all codes and \pzpdf s would be requested.
%The resulting catalogues contain $111\,171$ training galaxies and $1\,000\,883$ test galaxies.

@@

We aimed to provide template-fitting codes with complete yet manageable library of templates spanning the space of SEDs of the DC1 galaxies.
We constructed $K=100$ representative templates from the $\sim 5 \times 10^{5}$ SEDs of the \sdss\ DR6 NYU-VAGC by using the five-dimensional vectors of SED weight coefficients described above.
After regularizing the SED weight coefficients $\in [0, 1]$, we ran a simple K-means clustering algorithm on the five-dimensional space of regularized SED weight coefficients of the \sdss\ galaxy sample.
The resulting clusters were used to define Voronoi cells in the space of weight coefficients, with centre positions corresponding to weights for the \texttt{k-correct} SED components, yielding 100 templates to be provided to all template-based codes.
We did not, however, exclude from consideration template-based codes that made modifications in their use of these templates due to architecture limitations (as opposed to knowledge of the experimental conditions that could artificially boost the code's apparent performance), with deviations noted in Section~\ref{sec:pzcodes}.

>>>>

To assign a spectrum to each galaxy, the Adding Density Dependent Spectral Energy Distributions (SEDs) procedure (\texttt{ADDSEDS}, deRose in prep.)\footnote{\url{https://github.com/vipasu/addseds}} was used.
\texttt{ADDSEDS} uses a sample of $\sim 5\times 10^{5}$ galaxies from the magnitude-limited \sdss\ Data Release 6 Value Added Galaxy Catalogue \citep{Blanton:05} to train an empirical relation between absolute $r$-band magnitude, local galaxy density, and SED.
Each \sdss\ spectrum is parameterized by five weights corresponding to a weighted sum of five basis SED components using the \texttt{k-correct \red{v4\_3?}} software package\footnote{\url{http://kcorrect.org}} \citep{Blanton:07}.

@@

Following the findings of \citet{Bernstein:10}, \citet{Masters:2017} that only $~10^{4}$ spectra are necessary to calibrate \pz s to Stage IV requirements, we aimed to set aside a randomly selected training set of $3-5\times 10^{4}$ galaxies, $\sim 10\%$ of the full sample.
After all cuts described above, we designated the \textit{DC1 training set} of $44\,404$ galaxies for which observed photometry, true SEDs, and true redshifts would be provided to all codes codes and the blinded \textit{DC1 test set} of $399\,356$ galaxies for which photometry alone would be provided to all codes and \pzpdf s would be requested.
%The resulting catalogues contain $111\,171$ training galaxies and $1\,000\,883$ test galaxies.

@@

We aimed to provide template-fitting codes with complete yet manageable library of templates spanning the space of SEDs of the DC1 galaxies.
We constructed $K=100$ representative templates from the $\sim 5 \times 10^{5}$ SEDs of the \sdss\ DR6 NYU-VAGC by using the five-dimensional vectors of SED weight coefficients described above.
After regularizing the SED weight coefficients $\in [0, 1]$, we ran a simple K-means clustering algorithm on the five-dimensional space of regularized SED weight coefficients of the \sdss\ galaxy sample.
The resulting clusters were used to define Voronoi cells in the space of weight coefficients, with centre positions corresponding to weights for the \texttt{k-correct} SED components, yielding the 100 \textit{DC1 template set} to be provided to all template-based codes.
We did not, however, exclude from consideration template-based codes that made modifications in their use of these templates due to architecture limitations (as opposed to knowledge of the experimental conditions that could artificially boost the code's apparent performance), with deviations noted in Section~\ref{sec:pzcodes}.
